supplmental

### 2019-12-31 paper_stats.Rmd
tables

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(knitr)
  library(pander)

@@

Table 1. Respondent characteristics
```{r table1_data}

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>%
  kable()

@@

Table 2. Blood pressure outcomes
```{r results = "asis"}

@@

Figure 1. Mixed-effect model estimated treatment effects for blood pressure outcomes. 
```{r}
# Produce a data frame of the estimates and 95%CI from the models and plot it

@@

Figure 2. Change in systolic blood pressure across the two study periods
```{r}

>>>>

  library(sjPlot)
  library(tidyverse)
  library(broom)
  library(knitr)
  library(pander)
  library(DT)

@@

Table 1. Respondent characteristics

```{r table1_data}

@@

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>%
  datatable()

@@

Table 2. Blood pressure outcomes

```{r results = "asis"}

@@

Figure 1. Mixed-effect model estimated treatment effects for blood pressure outcomes.

```{r}
# Produce a data frame of the estimates and 95%CI from the models and plot it

@@

Figure 2. Change in systolic blood pressure across the two study periods
